Patient-Specific Neural Field Model

### 2010-07-19 ltx/data_paper/DataPaper.tex
added the model reduction part to the paper

By assuming the synaptic response kernel has the form 

@@

The neural field equations must be written as a discrete-time finite-dimensional model in order to relate it to patient-specific data. The discrete time model is found applying the a first-order Euler method giving

@@

where $T_s$ is the time step or sampling period. Rearranging equation~\ref{EulerMethod} gives the integro-difference equation

@@

where $\xi = 1-T_s\zeta$.

\subsection{Data Collection and Pre-processing}
\begin{itemize}
	\item Show medical imaging
	\item Show LFP Data (background, seizure, post-seizure)
	\item Show spectral properties of LFPs
\end{itemize}

>>>>

By assuming the synaptic response kernel is of first order has the form of

@@

The neural field equations must be written as a discrete-time finite-dimensional model in order to relate it to patient-specific data. The discrete-time model is found applying the a first-order Euler method giving

@@

where $T_s$ is the time step or sampling period. Rearranging equation~\ref{EulerMethod} gives the integro-difference equation (IDE) form

@@

where $\xi = 1-T_s\zeta$. Finally, a disturbance term is added, to account for uncertainty and unmodelled inputs, to the IDE form giving
	\label{NoisyDiscreteTimeModel} 
	\textrm{d}\mathbf{r}'} 
	+ e_t\left(\mathbf{r}\right), 
where $e_t(\mathbf{r})$ is $i.i.d.$ such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}.
To reduce the model to a finite dimensional system the neural field is approximated by a basis function decomposition where
	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 
where $\mathbf{x}_t$ is a state vector that weights another vector of two-dimension Gaussian basis functions, $\boldsymbol{\phi}(\mathbf{r})$, described by
\begin{equation}\label{eq:FieldBasisFunction}
	\boldsymbol\phi\left(\mathbf{r}-\mathbf{r}'\right) =
\exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_{\phi}^2}\right)}. 
The parameter $\sigma_{\phi}$ controls the basis function width and is inferred by frequency analysis. Substituting equation~\ref{DefFieldDecomp} into~\ref{NoisyDiscreteTimeModel} gives to approximate model
	\label{eq:reduced continuous model}
	\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_{t+1}= T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )w(\mathbf{r}-\mathbf{r}')\textrm{d}\mathbf{r}'}
	+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})x_t + e_t(\mathbf{r}). 
Next we multiply equation~\ref{eq:reduced continuous model} by $\boldsymbol{\phi}(\mathbf{r})$ and integrate over the spatial domain, $\Omega$, to get 
	\label{StartofReduction}
 	\int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \textrm{d}\mathbf{r}} \mathbf{x}_{t+1} = T_s \int_\Omega {\boldsymbol{\phi} (\mathbf{r}) \int_\Omega {w(\mathbf{r}-\mathbf{r}') f(\boldsymbol{\phi}^{\top}(\mathbf{r}') \mathbf{x}_t ) \textrm{d}\mathbf{r}'}\textrm{d}\mathbf{r}} + \xi\int_\Omega{\boldsymbol{\phi}(\mathbf{r})\boldsymbol{\phi}^{\top}(\mathbf{r})\textrm{d}\mathbf{r}} \mathbf{x}_t + \int_\Omega{\boldsymbol{\phi} (\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}. 
Now by defining the matrix
\begin{equation}\label{eq:DefGamma}
	\boldsymbol{\Gamma} \triangleq \int_\Omega {\boldsymbol{\phi} \left(\mathbf{r}\right)\boldsymbol{\phi} ^{\top}\left(\mathbf{r}\right)\textrm{d}\mathbf{r}} 
enables the pseudo inverse of $\boldsymbol{\phi(\mathbf{r})}$ to be taken such that the state vector can is isolated on the left-hand-side as
\begin{equation}\label{eq:ReducedForm}
	 \mathbf{x}_{t+1} = T_s\boldsymbol{\Gamma}^{-1}
	 \int_\Omega \boldsymbol{\phi}(\mathbf{r}) 
	 \int_\Omega w(\mathbf{r}-\mathbf{r}')f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t) \textrm{d}\mathbf{r}' \textrm{d}\mathbf{r} 
	 + \xi\mathbf{x}_t + \boldsymbol{\Gamma}^{-1} \int_\Omega{\boldsymbol{\phi}(\mathbf{r}) e_t(\mathbf{r})\textrm{d}\mathbf{r}}.
\subsection{Data Collection and Pre-processing}
\begin{itemize}
	\item Show medical imaging
	\item Show LFP Data (background, seizure, post-seizure)
	\item Show spectral properties of LFPs
\end{itemize}
